---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

ipv4heatmap : Generate Hilbert Curve Heatmaps from IPv4 Address Lists

The following functions are implemented:

- `boundingBoxFromCIDR`:	Bounding box from CIDR blocks
- `ip2long`:	Character (dotted-decimal) IPv4 Address Conversion to long integer
- `ipv4heatmap`:	Create an IPv4 Hilbert curve heatmap
- `ipv4matrix`:	IPv4 Hilbert Curve Matrix
- `long2ip`:	Intger IPv4 Address Conversion to Character

### News

- 0.2.0.999 - No longer requires Boost libraries, passes CRAN checks

### Installation

```{r install, eval=FALSE}
devtools::install_github("hrbrmstr/ipv4heatmap")
```

```{r options_2, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=200)
```

### Usage

```{r usage}
library(ipv4heatmap)

# current verison
packageVersion("ipv4heatmap")

(ip2long(c( "105.212.209.72", "115.126.247.136")))

(long2ip(c(1775554888, 1937700744)))

(boundingBoxFromCIDR("30.0.0.0/8"))

# get and plot some IPs from ZeusTracker
loc <- tempfile()
download.file("https://zeustracker.abuse.ch/blocklist.php?download=badips", 
              loc, method="curl")
ips <- grep("^#", readLines(loc), invert=TRUE, value=TRUE)
unlink(loc)

hm <- ipv4heatmap(ips)

hm$gg
```

### Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
